Fractional Decomposition Tree Algorithm: A tool for studying the integrality gap of Integer Programs

### 2020-08-07 FDT2020/Introduction.tex
comments replied

%\arash{I added this figure \ref{fig:CVpoint} but maybe we can put it later in the experiments section to make the introduction shorter?} \cindy{Yes that would be fine, if the reader could also use that figure then.  They could page forward to see the figure when reading the introduction.}

Carr and Vempala \cite{Carr2004} showed that $g(\2ec)$ is achieved for instances where the optimal solution to $\min_{x\in \subtour(G)}cx$ is a Carr-Vempala point. We show that the integrality gap is at most $\frac{6}{5}$ for Carr-Vempala points with at most 12 vertices on the cycle formed by the fractional edges.
\cindy{This sounds like a contribution of the paper.} \arash{Yes, particlarly since a similar research question have been studied by \cite{alexander2006integrality} and \cite{TSPcompute}}
Note that the number of vertices in these instances can be arbitrarily high since the paths of edges with $x$-value 1 can be arbitrarily long.

>>>>

%\arash{I added this figure \ref{fig:CVpoint} but maybe we can put it later in the experiments section to make the introduction shorter?} \cindy{Yes that would be fine, if the reader could also use that figure then.  They could page forward to see the figure when reading the introduction.}
\arash{I changed the paragraph below a little bit, can you check?}
Carr and Vempala \cite{Carr2004} showed that $g(\2ec)$ is achieved for instances where the optimal solution to $\min_{x\in \subtour(G)}cx$ is a Carr-Vempala point. It has be conjectured that $g(\2ec)\leq \frac{6}{5}$ (see \cite{alexander2006integrality,boydlegault,hn19}, but the only known upper bound on $g(\2ec)$ stands at $\frac{3}{2}$ \cite{wolsey}. We show that the integrality gap is at most $\frac{6}{5}$ for Carr-Vempala points with at most 12 vertices on the cycle formed by the fractional edges, thereby confirming the conjecture for these instances.
\cindy{This sounds like a contribution of the paper.} \arash{Yes, particlarly since a similar research question have been studied by \cite{alexander2006integrality} and \cite{TSPcompute}}
Note that the number of vertices in these instances can be arbitrarily high since the paths of edges with $x$-value 1 can be arbitrarily long.

### 2020-08-07 FDT2020/main-section.tex
comments replied

Consider an instance $I=(A,b)$ of the IP formulation. Define sets $S(I)$ and $P(I)$ as in (\ref{S}) and (\ref{P}), respectively. Assume $S(I)\subseteq \{0,1\}^n$ and $P(I)\subseteq [0,1]^n$. For simplicity in the notation we assume an instance $I$ and denote $P(I),S(I),$ and $g(I)$ by $P$, $S$, and $g$ for this section and the next section. Also, for both sections we assume $t=|\spp(x)|$. Without loss of generality we can assume $x_i = 0$ for $i=t+1,\ldots,n$.
\cindy{TODO: Is this something that should be clear to the reader with what they know at this point? Does it need an explanation? Does it need an explanation at the end of this section or the next?}\arash{this is just a relabeling of the indices.} \cindy{Sorry.  I didn't understand that you meant the solution has that property. Right? The vector $x$ isn't defined in this paragraph and it's not in the next lemma either. If $x$ is the output of DomToIP, then we should say that.  ``Without loss of generality the solution $x$ returned by DomToIP has ...''}

In this section we prove Theorem \ref{domtoIP}. In fact, we prove a stronger result. 
\begin{lemma}\label{domlemma}
	Given $\tilde{x}\in \dom(P)$ and $\tilde{x}\in \{0,1\}^n$, there is an algorithm (the DomToIP algorithm) that finds $\bar{x}\in S$ in polynomial time, such that $\bar{x}\leq \tilde{x}$.\end{lemma}
Notice that Lemma \ref{domlemma} implies Theorem \ref{domtoIP}, since it is easy to obtain an integer point in $\dom(P)$: numerically rounding up any fractional point in $P$ gives us a point in $\dom(P)$.

\subsection{Proof of Lemma \ref{domlemma}: The DomToIP Algorithm}

@@

\section{FDT on Binary IPs}
\label{sec:binaryfdt}

Assume we are given a point $x^*\in P$. For instance, $x^*$ can be the optimal solution of minimizing a cost function $cx$ over set $P$, which provides a lower bound on $\min_{(x,y)\in S(I)} cx$.  In this section, we prove Theorem \ref{binaryFDT} by describing the Fractional Decomposition Tree (FDT) algorithm. We also remark that if $g(I)=1$, then the algorithm will give an exact decomposition of any feasible solution.

>>>>

Consider an instance $I=(A,b)$ of the IP formulation. Define sets $S(I)$ and $P(I)$ as in (\ref{S}) and (\ref{P}), respectively. Assume $S(I)\subseteq \{0,1\}^n$ and $P(I)\subseteq [0,1]^n$. For simplicity in the notation we assume an instance $I$ and denote $P(I),S(I),$ and $g(I)$ by $P$, $S$, and $g$ for this section and the next section. Also, for both sections let $x^*$ be the optimal solution to the LP formulation and assume $t=|\spp(x^*)|$. Without loss of generality we can assume $x^*_i = 0$ for $i=t+1,\ldots,n$.
\cindy{TODO: Is this something that should be clear to the reader with what they know at this point? Does it need an explanation? Does it need an explanation at the end of this section or the next?}\arash{this is just a relabeling of the indices.} \cindy{Sorry.  I didn't understand that you meant the solution has that property. Right? The vector $x$ isn't defined in this paragraph and it's not in the next lemma either. If $x$ is the output of DomToIP, then we should say that.  ``Without loss of generality the solution $x$ returned by DomToIP has ...''}\arash{I see your point, please see if the change made it better}

In this section we prove Theorem \ref{domtoIP}. In fact, we prove a stronger result. 
\begin{lemma}\label{domlemma}
	Given $\tilde{x}\in \dom(P)$ and $\tilde{x}\in \{0,1\}^n$, there is an algorithm (the DomToIP algorithm) that finds $\bar{x}\in S$ in polynomial time, such that $\bar{x}\leq \tilde{x}$.\end{lemma}
Notice that Lemma \ref{domlemma} implies Theorem \ref{domtoIP}, since it is easy to obtain an integer point in $\dom(P)$: numerically rounding up $x^*$ (or any fractional point in $P$) gives us a point in $\dom(P)$. Hence, we can assume in the proof below that $\tilde{x}_i= 0$ for $i=t+1,\ldots,n$. 
\arash{I also made a change based on the change above}
\subsection{Proof of Lemma \ref{domlemma}: The DomToIP Algorithm}

@@

\section{FDT on Binary IPs}
\label{sec:binaryfdt}
\arash{I made a small change here based on our discussion in the bottom of page 8}
Recall that $x^*$ was the optimal solution of minimizing a cost function $cx$ over set $P$, which provides a lower bound on $\min_{(x,y)\in S(I)} cx$.  In this section, we prove Theorem \ref{binaryFDT} by describing the Fractional Decomposition Tree (FDT) algorithm. We also remark that if $g(I)=1$, then the algorithm will give an exact decomposition of any feasible solution.
